\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in \proglang{R}

### 2014-11-19 papers/jss/article.Rnw
Make section 4 more concise and less manual-like per referee #1 feedback.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@902 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

<<>>=
tutorial.Person$email

tutorial.Person$PhoneType

tutorial.Person$PhoneNumber

tutorial.Person.PhoneNumber
@

\subsection{Field descriptors}
\label{subsec-field-descriptor}

The class \emph{FieldDescriptor} represents field
descriptors in \proglang{R}. This is a wrapper S4 class around the
\code{google::protobuf::FieldDescriptor} \proglang{C++} class.

<<>>=
tutorial.Person$email
tutorial.Person$email$is_required()
tutorial.Person$email$type()
tutorial.Person$email$as.character()
@

\subsection{Enum descriptors}
\label{subsec-enum-descriptor}

The class \emph{EnumDescriptor} represents enum descriptors in \proglang{R}.
This is a wrapper S4 class around the
\code{google::protobuf::EnumDescriptor} \proglang{C++} class.

The \verb|$| operator can be used to retrieve the value of enum
constants contained in the EnumDescriptor, or to invoke
methods.

The \code{EnumDescriptor} contains information about what values this type
defines, while the \code{EnumValueDescriptor} describes an
individual enum constant of a particular type.

<<>>=
tutorial.Person$PhoneType
tutorial.Person$PhoneType$WORK
@

\subsection{Enum value descriptors}
\label{subsec-enumvalue-descriptor}

The class \emph{EnumValueDescriptor} represents enumeration value
descriptors in \proglang{R}.  This is a wrapper S4 class around the
\code{google::protobuf::EnumValueDescriptor} \proglang{C++} class.

The \verb|$| operator can be used to invoke methods.

<<>>=
tutorial.Person$PhoneType$value(1)
tutorial.Person$PhoneType$value(name="HOME")
tutorial.Person$PhoneType$value(number=1)
@

\subsection{File descriptors}
\label{subsec-file-descriptor}

The class \emph{FileDescriptor} represents file descriptors in \proglang{R}.
This is a wrapper S4 class around the
\code{google::protobuf::FileDescriptor} \proglang{C++} class.

The \verb|$| operator can be used to retrieve named fields defined in
the FileDescriptor, or to invoke methods.

>>>>

\subsubsection*{Field descriptors}
\label{subsec-field-descriptor}

<<>>=
tutorial.Person$email 
tutorial.Person$email$is_required()
tutorial.Person$email$type()
tutorial.Person$email$as.character()
class(tutorial.Person$email)
@

\subsubsection*{Enum and EnumValue descriptors}
\label{subsec-enum-descriptor}

The \code{EnumDescriptor} contains information about what values a
type defines, while the \code{EnumValueDescriptor} describes an
individual enum constant of a particular type.  The \verb|$| operator
can be used to retrieve the value of enum constants contained in the
EnumDescriptor, or to invoke methods.

<<>>=
tutorial.Person$PhoneType
tutorial.Person$PhoneType$WORK
class(tutorial.Person$PhoneType)
tutorial.Person$PhoneType$value(1)
tutorial.Person$PhoneType$value(name="HOME")
tutorial.Person$PhoneType$value(number=1)
class(tutorial.Person$PhoneType$value(1))
@

\subsubsection*{File descriptors}
\label{subsec-file-descriptor}

The class \emph{FileDescriptor} represents file descriptors in \proglang{R}.
The \verb|$| operator can be used to retrieve named fields defined in
the FileDescriptor, or to invoke methods.
